Field work 2016

### 2016-11-30 analysis/geo2.Rmd
updating

---
title: "Field work"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    orientation: rows
---

@@

```{r pacakges}
library('rgdal')
library("leaflet") 
library("sp")
library("raster")

library('dplyr')

library('ggplot2')

>>>>

---
title: "Field work 2016"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    orientation: rows
---

@@

```{r pacakges}
library('rgdal')
library("leaflet") 
library("sp")
library("raster")
library('dplyr')
library('ggplot2')
```
